Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-04-16 Paper/paper.tex
Update text

\author[Kulkarni et al.]{{Girish Kulkarni$^{1}$\thanks{Email:
      kulkarni@ast.cam.ac.uk}, G\'abor Worseck$^{2}$ and Joseph
    F.~Hennawi$^{3}$} \\ $^1$Institute of Astronomy and Kavli
  Institute of Cosmology, University of Cambridge, Madingley Road,
  Cambridge CB3 0HA, UK \\ $^2$Institute f\"ur Physik und Astronomie,
  Universit\"at Potsdam, Karl-Liebknecht-Str.\ 24/25, 14476 Potsdam,
  Germany\\ $^3$Department of Physics, Broida Hall, UC Santa Barbara,
  Santa Barbara, CA 93106-9530 USA}
\date{Accepted ---. Received ---; in original form ---}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{qsos.pdf}
    % data.py 
  \end{center}
  \caption{Redshift distribution of the XX quasars considered in this
    analysis.  Shown here are the observed quasar numbers, without
    correcting for incompleteness.  Further details on each of these
    data sets are in Table~\ref{tab:samples} and
    Section~\ref{sec:sample}.}
  \label{fig:qsos}
\end{figure*}

@@

  % bins_tabulate.py; Nqso added by hand
  \caption{Best-fit double power law luminosity function parameters in
    various redshift bins.  The luminosity function parameters
    $\phi_*$, $M_*$, $\alpha$, and $\beta$ are defined in
    Equation~(\ref{eqn:dpl}), with $\beta$ denoting the faint-end
    slope.  Quasars in each bin have redshifts $z_\mathrm{min}\leq z <
    z_\mathrm{max}$.  The number of quasars in each bin is given by
    $N_\mathrm{qso}$.  The bin centre and sample mean redshift are
    given by $z_\mathrm{bin}$ and $\langle z\rangle$, respectively.
    Errors indicate one-sigma (68.26\%) uncertainties.  These values
    are shown in Figure~\ref{fig:evoln}.  The corresponding luminosity
    functions are shown in Figure~\ref{fig:mosaic}.  See
    Section~\ref{sec:bins} for further details.}
  \label{tab:bins}
  \begin{tabular}{ccccrcccc}
    $\langle z\rangle$ & $z_\mathrm{bin}$ & $z_\mathrm{min}$ & $z_\mathrm{max}$ & $N_\mathrm{qso}$ & $\log_{10}(\phi_*/$ & $M_*$ & $\alpha$ & $\beta$ \\
    & & & & & cMpc$^{-3}$mag$^{-1}$) & & & \\
    $0.31$ & $0.25$ & $0.10$ & $0.40$ & 3520 & $-5.62^{+0.09}_{-0.10}$ & $-21.37^{+0.21}_{-0.22}$ & $-2.94^{+0.09}_{-0.10}$ & $-1.22^{+0.18}_{-0.16}$ \\
    $0.50$ & $0.50$ & $0.40$ & $0.60$ & 4555 & $-6.12^{+0.04}_{-0.04}$ & $-23.00^{+0.08}_{-0.08}$ & $-3.37^{+0.07}_{-0.08}$ & $-1.36^{+0.04}_{-0.04}$ \\
    $0.72$ & $0.70$ & $0.60$ & $0.80$ & 3308 & $-6.42^{+0.09}_{-0.08}$ & $-24.03^{+0.15}_{-0.13}$ & $-3.55^{+0.12}_{-0.13}$ & $-1.75^{+0.05}_{-0.04}$ \\
    $0.91$ & $0.90$ & $0.80$ & $1.00$ & 3922 & $-6.39^{+0.08}_{-0.07}$ & $-24.51^{+0.12}_{-0.11}$ & $-3.69^{+0.10}_{-0.11}$ & $-1.73^{+0.06}_{-0.05}$ \\
    $1.10$ & $1.10$ & $1.00$ & $1.20$ & 6367 & $-6.53^{+0.03}_{-0.03}$ & $-25.14^{+0.04}_{-0.04}$ & $-4.17^{+0.08}_{-0.09}$ & $-1.73^{+0.02}_{-0.02}$ \\
    $1.30$ & $1.30$ & $1.20$ & $1.40$ & 6479 & $-6.43^{+0.04}_{-0.04}$ & $-25.29^{+0.06}_{-0.06}$ & $-3.97^{+0.08}_{-0.08}$ & $-1.74^{+0.03}_{-0.03}$ \\
    $1.50$ & $1.50$ & $1.40$ & $1.60$ & 7539 & $-6.51^{+0.03}_{-0.03}$ & $-25.68^{+0.04}_{-0.04}$ & $-4.28^{+0.08}_{-0.08}$ & $-1.75^{+0.02}_{-0.02}$ \\
    $1.71$ & $1.70$ & $1.60$ & $1.80$ & 6788 & $-6.28^{+0.04}_{-0.04}$ & $-25.55^{+0.05}_{-0.05}$ & $-3.96^{+0.07}_{-0.07}$ & $-1.60^{+0.03}_{-0.03}$ \\
    $1.98$ & $2.00$ & $1.80$ & $2.20$ & 10478 & $-6.72^{+0.03}_{-0.03}$ & $-26.26^{+0.04}_{-0.04}$ & $-4.20^{+0.07}_{-0.07}$ & $-1.87^{+0.02}_{-0.02}$ \\
    $2.25$ & $2.25$ & $2.20$ & $2.30$ & 4102 & $-5.98^{+0.10}_{-0.09}$ & $-25.26^{+0.19}_{-0.18}$ & $-3.21^{+0.15}_{-0.16}$ & $-1.54^{+0.07}_{-0.06}$ \\
    $2.35$ & $2.35$ & $2.30$ & $2.40$ & 4317 & $-6.28^{+0.09}_{-0.09}$ & $-25.63^{+0.17}_{-0.15}$ & $-3.39^{+0.17}_{-0.19}$ & $-1.64^{+0.06}_{-0.05}$ \\
    $2.45$ & $2.45$ & $2.40$ & $2.50$ & 3403 & $-6.40^{+0.08}_{-0.07}$ & $-25.86^{+0.14}_{-0.13}$ & $-3.60^{+0.20}_{-0.21}$ & $-1.60^{+0.05}_{-0.05}$ \\
    $2.65$ & $2.65$ & $2.60$ & $2.70$ & 1883 & $-5.98^{+0.06}_{-0.06}$ & $-25.15^{+0.14}_{-0.13}$ & $-3.13^{+0.12}_{-0.13}$ & $-1.05^{+0.09}_{-0.08}$ \\
    $2.75$ & $2.75$ & $2.70$ & $2.80$ & 1135 & $-6.30^{+0.08}_{-0.07}$ & $-25.96^{+0.15}_{-0.13}$ & $-3.81^{+0.28}_{-0.31}$ & $-1.34^{+0.07}_{-0.06}$ \\
    $2.85$ & $2.85$ & $2.80$ & $2.90$ & 1069 & $-6.46^{+0.12}_{-0.10}$ & $-26.23^{+0.23}_{-0.18}$ & $-3.60^{+0.36}_{-0.42}$ & $-1.46^{+0.08}_{-0.07}$ \\
    $2.95$ & $2.95$ & $2.90$ & $3.00$ & 1104 & $-6.77^{+0.07}_{-0.06}$ & $-26.53^{+0.10}_{-0.09}$ & $-5.05^{+0.60}_{-0.64}$ & $-1.71^{+0.05}_{-0.04}$ \\
    $3.05$ & $3.05$ & $3.00$ & $3.10$ & 1127 & $-6.77^{+0.08}_{-0.07}$ & $-26.48^{+0.12}_{-0.10}$ & $-4.71^{+0.46}_{-0.52}$ & $-1.70^{+0.06}_{-0.05}$ \\
    $3.15$ & $3.15$ & $3.10$ & $3.20$ & 1041 & $-7.25^{+0.17}_{-0.12}$ & $-27.09^{+0.25}_{-0.18}$ & $-4.42^{+0.81}_{-1.23}$ & $-1.96^{+0.08}_{-0.06}$ \\
    $3.25$ & $3.25$ & $3.20$ & $3.30$ & 815 & $-7.33^{+0.13}_{-0.13}$ & $-27.19^{+0.19}_{-0.23}$ & $-4.36^{+0.65}_{-0.76}$ & $-1.93^{+0.06}_{-0.06}$ \\
    $3.34$ & $3.35$ & $3.30$ & $3.40$ & 510 & $-7.54^{+0.19}_{-0.21}$ & $-27.39^{+0.25}_{-0.37}$ & $-4.90^{+1.36}_{-1.35}$ & $-2.08^{+0.09}_{-0.07}$ \\
    $3.44$ & $3.45$ & $3.40$ & $3.50$ & 155 & $-6.77^{+0.19}_{-0.20}$ & $-26.64^{+0.42}_{-0.35}$ & $-3.70^{+0.62}_{-0.80}$ & $-1.24^{+0.27}_{-0.22}$ \\
    $3.88$ & $3.90$ & $3.70$ & $4.10$ & 628 & $-7.92^{+0.12}_{-0.10}$ & $-27.26^{+0.14}_{-0.12}$ & $-4.81^{+0.34}_{-0.39}$ & $-2.07^{+0.10}_{-0.09}$ \\
    $4.35$ & $4.40$ & $4.10$ & $4.70$ & 442 & $-8.32^{+0.29}_{-0.26}$ & $-27.38^{+0.38}_{-0.31}$ & $-4.19^{+0.41}_{-0.47}$ & $-2.20^{+0.16}_{-0.13}$ \\
    $4.92$ & $5.10$ & $4.70$ & $5.50$ & 263 & $-9.02^{+0.29}_{-0.22}$ & $-27.88^{+0.36}_{-0.27}$ & $-4.51^{+0.66}_{-0.83}$ & $-2.31^{+0.11}_{-0.08}$ \\
    $6.00$ & $6.00$ & $5.50$ & $6.50$ & 66 & $-10.60^{+0.71}_{-1.06}$ & $-29.12^{+1.04}_{-1.78}$ & $-4.99^{+0.72}_{-1.22}$ & $-2.40^{+0.10}_{-0.08}$ \\

@@

Figure~\ref{fig:evoln} reveals further potentially systematic errors.
The behaviour of BOSS quasars, shown by open circles in
Figure~\ref{fig:evoln} at redshifts $z=2$--$4$ is striking.  In this
redshift range covered by BOSS the values of the four double power law
parameters deviate from the general trends.  The faint end of the
luminosity function of the BOSS quasars is much shallower and the
break luminosity is fainter by a magnitude compared to the general
trend expected from a smooth evolution.  The bright end of the
luminosity function of quasars in this sample is also much flatter
than that for other samples.  The conspicuousness of the deviation of
the BOSS sample from the general trends makes it unlikely that the
luminosity function evolution indicated by BOSS in the redshift range
$z=2$--$3$ is physical.  Indeed, in this redshift range BOSS quasar
selection is known to be affected by a colour bias
\citep{2011ApJ...728...23W}, which can make estimating completeness
difficult \citep{2006AJ....131.2766R}.  \gk{Gabor, could you please
  check if I have written this paragraph OK?}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
    % mosaic.py 
  \end{center}
  \caption{Luminosity function estimates from $z=0.3$ to $2.6$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, the yellow
    curves show the best-fit double power law luminosity function in
    that redshift bin.  The green curves show the posterior
    distribution of the global model.  The global model agrees very
    well with the data in all redshift bins, except those spanned by
    BOSS, as BOSS quasars are excluded from the global
    analysis. \gk{Show all three models here.}}
  \label{fig:mosaic_global}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    model.  The symbols show the best fit parameters with 68\%
    uncertainties from the double power law fits to the data in
    redshift bins.  These points are identical to those in
    Figure~\ref{fig:evoln}, except that bins with BOSS qsos ($z\sim
    2$--$3$) are not shown.  In each panel, the black solid curve
    shows the best fit global model, and the coloured curves show a
    random sample drawn from the global posterior. \gk{Cannot see
      best-fit curves.  Add open and closed circles to legend.}}
  \label{fig:evoln_global}
\end{figure*}

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
    % rhoqso.py -- draw_withGlobal()
  \end{center}
  \caption{AGN number density evolution in the global model.  Similar
    to Figure~\ref{fig:evoln_global}, symbols show the best fit
    parameters with 68\% uncertainties from the double power law fits
    to the data in redshift bins.  Black solid curve shows the best
    fit global model, and the coloured curves show a random sample
    drawn from the global posterior. \gk{I still think we should show
      the $-18$ case here.  Mention magnitude limits.  Reduce
      transarency.  Extend plot to at least redshift 7.5.  Increase
      legend handle length to match other figure. Should we add French
      curve fits to this?}}
  \label{fig:rhoqso}
\end{figure}

@@

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.47\textwidth]{emissivity_18.pdf} & 
      \includegraphics[width=0.47\textwidth]{emissivity_21.pdf} \\
      % gammapi.py -- draw_emissivity()
    \end{tabular}
  \end{center}
  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
    fraction down to a limiting magnitude for a luminosity function
    integration limit of $M_{1450}=-18$ (left panel) and
    $M_{1450}=-21$ (right panel).  Black filled circles with error
    bars in both panels show the emissivity determinations in redshift
    bin deemed to have low systematic errors.  Open circles show
    emissivities for redshift bins that we remove from analysis due to
    high systematic errors.  Solid red curves in both panels show the
    best fit emissivity evolution model, with the shaded area showing
    the one-sigma (68.26\%) uncertainty.  Also shown for comparison in
    both panels are models by \citet[pentagon
      symbol]{2009A&A...507..781S}, \citet[star]{2012ApJ...755..169M},
    \citet[square]{2015AA...578A..83G},
    \citet[triangle]{2018PASJ...70S..34A},
    \citet[circle]{2018AJ....155..131M},
    \citet[diamond]{2018MNRAS.474.2904P}, \citet[open
      rectangle]{2017ApJ...847L..15O}, \citet[dotted green
      curve]{2015ApJ...813L...8M}, \citet[dashed
      brown]{2012ApJ...746..125H}, \citet[dashed
      grey]{2017MNRAS.466.1160M}, \citet[dashed
      blue]{2013A&A...551A..29P}, \citet[solid
      cyan]{2016A&A...587A..41P}, and \citet[solid
      blue]{2017A&A...608A..64C}}
  \label{fig:e912_2}
\end{figure*}

\subsection{Evolution of the luminosity function}

The smooth evolution of the luminosity function parameters apparant in
Figure~\ref{fig:evoln} suggests that it should be possible to describe
the quasar UV luminosity function evolution out to $z\sim 7$ using far
fewer number of parameters.  Such descriptions have been developed in
the literature for the X-ray \citep[e.g.,][]{2015MNRAS.451.1892A} and
bolometric luminosity functions \citep[e.g.,][]{2007ApJ...654..731H}.
Such ``global'' descriptions of the luminosity function evolution are
useful as they give a continuous description of the luminosity
function.  This allows one to reduce the bias introduced by binning
the data in arbitrary redshift bins.  By potentially allowing for
extrapolations beyond the redshift range spanned by the data, such
models are valuable for understanding of the physics behind the
luminosity function.  Ideally, one would want to use physically
meaningful parameters that govern the formation and evolution of the
AGN population.  Unfortunately, such physical parameterisation is yet
to be developed.  We therefore set up an empirical parameterisation to
describe the evolution of the four parameters of the double power law
model in Equation~(\ref{eqn:dpl}) as 
\begin{align}
  &\phi_*(z) = f_0(\{c_{0,i}\}, z)\nonumber\\
  &M_*(z) = f_1(\{c_{1,i}\}, z)\nonumber\\
  &\alpha(z) = f_2(\{c_{2,i}\}, z)\nonumber\\
  &\beta(z) = f_3(\{c_{3,i}\}, z),
\label{eqn:global}
\end{align}
where the $c_{j,i}$'s are the new model parameters, and the $f_j$'s
are functions that vary smoothly with redshift $z$.  The joint
posterior probability distribution of these parameters can be now
written as
\begin{equation}
  p(\{c_i\} | \{M_i, z_i\}) \propto p(\{c_i\})p(\{M_i, z_i\} | \{c_i\}),
\end{equation}
where the likelihood 
\begin{equation}
  \mathcal{L}\equiv p(\{M_i, z_i\} | \{c_i\}),
\end{equation}
is now given by $\phi(M,z)$ with suitable normalisation.  Note that
$\phi(M,z)$ is given by Equation~(\ref{eqn:dpl}), but now the four
parameters in that equation are redshift-dependent, so that
\begin{multline}
  \phi(M,z) = \phi_*(z) \left[10^{0.4(\alpha(z)+1)(M-M_*(z))}\right. \\ \left.+ 10^{0.4(\beta(z)+1)(M-M_*(z))}\right]^{-1}.
\end{multline}
The negative logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ is
straightforward generalisation of Equation~(\ref{eqn:S}), given by 
\begin{multline}
  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
  \label{eqn:S2}
\end{multline}
where now $N$ is the total number of quasars included in the analysis,
and the integrals in the second term on the right-hand side are over
the complete surveyed range of luminosity and redshift, instead of
redshift and luminosity bins.  We consider models in which the
evolution of the four double power law parameter is modelled
independently as in Equations~(\ref{eqn:global}).  This approach has
been termed as ``flexible double power law'' by
\citet{2015MNRAS.451.1892A}.  We present three such models in this
paper.  These are shown in Figure~\ref{fig:evoln_global}.  The three
models differ in the way they describe the evolution of the faint-end
slope $\beta$ and in the selection of the AGN data.  The models are
defined as follows.

>>>>

\author[Kulkarni et al.]{{Girish Kulkarni$^{1}$\thanks{Email:
      kulkarni@ast.cam.ac.uk}, G\'abor Worseck$^{2}$ and Joseph
    F.~Hennawi$^{3}$} \\ $^1$Institute of Astronomy and Kavli
  Institute of Cosmology, University of Cambridge, Madingley Road,
  Cambridge CB3 0HA, UK \\ $^2$Institute f\"ur Physik und Astronomie,
  Universit\"at Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, 14476 Potsdam,
  Germany\\ $^3$Department of Physics, Broida Hall, UC Santa Barbara,
  Santa Barbara, CA 93106-9530 USA}
\date{Accepted ---. Received ---; in original form ---}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{qsos.pdf}
    % data.py 
  \end{center}
  \caption{Redshift distribution of the 86,015 AGN considered in this
    analysis.  Shown here are the observed quasar numbers, without
    correcting for incompleteness.  Further details on each of these
    data sets are in Table~\ref{tab:samples} and
    Section~\ref{sec:sample}.}
  \label{fig:qsos}
\end{figure*}

@@

\begin{table*}
  % bins_tabulate.py; Nqso added by hand
  \caption{Best-fit double power law luminosity function parameters in
    various redshift bins.  The luminosity function parameters
    $\phi_*$, $M_*$, $\alpha$, and $\beta$ are defined in
    Equation~(\ref{eqn:dpl}), with $\beta$ denoting the faint-end
    slope.  Quasars in each bin have redshifts $z_\mathrm{min}\leq z <
    z_\mathrm{max}$.  The number of quasars in each bin is given by
    $N_\mathrm{qso}$.  The bin centre and sample mean redshift are
    given by $z_\mathrm{bin}$ and $\langle z\rangle$, respectively.
    Errors indicate one-sigma (68.26\%) uncertainties.  These values
    are shown in Figure~\ref{fig:evoln}.  The corresponding luminosity
    functions are shown in Figure~\ref{fig:mosaic}.  See
    Section~\ref{sec:bins} for further details.}
  \label{tab:bins}
  \begin{tabular}{ccccr....}
    \hline
    $\langle z\rangle$ &
    $z_\mathrm{bin}$ &
    $z_\mathrm{min}$ &
    $z_\mathrm{max}$ &
    $N_\mathrm{qso}$ &
    \multicolumn{1}{c}{$\log_{10}(\phi_*/$} &
    \multicolumn{1}{c}{$M_*$} &
    \multicolumn{1}{c}{$\alpha$} &
    \multicolumn{1}{c}{$\beta$} \\

    &
    &
    &
    &
    &
    \multicolumn{1}{c}{cMpc$^{-3}$mag$^{-1}$)} &
    &
    & \\
    \hline
    0.31 & 0.25 & 0.10 & 0.40 & 3520 & -5.62^{+0.09}_{-0.10} & -21.37^{+0.21}_{-0.22} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
    0.50 & 0.50 & 0.40 & 0.60 & 4555 & -6.12^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.08} & -3.37^{+0.07}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
    0.72 & 0.70 & 0.60 & 0.80 & 3308 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.15}_{-0.13} & -3.55^{+0.12}_{-0.13} & -1.75^{+0.05}_{-0.04} \\
    0.91 & 0.90 & 0.80 & 1.00 & 3922 & -6.39^{+0.08}_{-0.07} & -24.51^{+0.12}_{-0.11} & -3.69^{+0.10}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
    1.10 & 1.10 & 1.00 & 1.20 & 6367 & -6.53^{+0.03}_{-0.03} & -25.14^{+0.04}_{-0.04} & -4.17^{+0.08}_{-0.09} & -1.73^{+0.02}_{-0.02} \\
    1.30 & 1.30 & 1.20 & 1.40 & 6479 & -6.43^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.06} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
    1.50 & 1.50 & 1.40 & 1.60 & 7539 & -6.51^{+0.03}_{-0.03} & -25.68^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.75^{+0.02}_{-0.02} \\
    1.71 & 1.70 & 1.60 & 1.80 & 6788 & -6.28^{+0.04}_{-0.04} & -25.55^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
    1.98 & 2.00 & 1.80 & 2.20 & 10478 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.20^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
    2.25 & 2.25 & 2.20 & 2.30 & 4102 & -5.98^{+0.10}_{-0.09} & -25.26^{+0.19}_{-0.18} & -3.21^{+0.15}_{-0.16} & -1.54^{+0.07}_{-0.06} \\
    2.35 & 2.35 & 2.30 & 2.40 & 4317 & -6.28^{+0.09}_{-0.09} & -25.63^{+0.17}_{-0.15} & -3.39^{+0.17}_{-0.19} & -1.64^{+0.06}_{-0.05} \\
    2.45 & 2.45 & 2.40 & 2.50 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.13} & -3.60^{+0.20}_{-0.21} & -1.60^{+0.05}_{-0.05} \\
    2.65 & 2.65 & 2.60 & 2.70 & 1883 & -5.98^{+0.06}_{-0.06} & -25.15^{+0.14}_{-0.13} & -3.13^{+0.12}_{-0.13} & -1.05^{+0.09}_{-0.08} \\
    2.75 & 2.75 & 2.70 & 2.80 & 1135 & -6.30^{+0.08}_{-0.07} & -25.96^{+0.15}_{-0.13} & -3.81^{+0.28}_{-0.31} & -1.34^{+0.07}_{-0.06} \\
    2.85 & 2.85 & 2.80 & 2.90 & 1069 & -6.46^{+0.12}_{-0.10} & -26.23^{+0.23}_{-0.18} & -3.60^{+0.36}_{-0.42} & -1.46^{+0.08}_{-0.07} \\
    2.95 & 2.95 & 2.90 & 3.00 & 1104 & -6.77^{+0.07}_{-0.06} & -26.53^{+0.10}_{-0.09} & -5.05^{+0.60}_{-0.64} & -1.71^{+0.05}_{-0.04} \\
    3.05 & 3.05 & 3.00 & 3.10 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.10} & -4.71^{+0.46}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
    3.15 & 3.15 & 3.10 & 3.20 & 1041 & -7.25^{+0.17}_{-0.12} & -27.09^{+0.25}_{-0.18} & -4.42^{+0.81}_{-1.23} & -1.96^{+0.08}_{-0.06} \\
    3.25 & 3.25 & 3.20 & 3.30 & 815 & -7.33^{+0.13}_{-0.13} & -27.19^{+0.19}_{-0.23} & -4.36^{+0.65}_{-0.76} & -1.93^{+0.06}_{-0.06} \\
    3.34 & 3.35 & 3.30 & 3.40 & 510 & -7.54^{+0.19}_{-0.21} & -27.39^{+0.25}_{-0.37} & -4.90^{+1.36}_{-1.35} & -2.08^{+0.09}_{-0.07} \\
    3.44 & 3.45 & 3.40 & 3.50 & 155 & -6.77^{+0.19}_{-0.20} & -26.64^{+0.42}_{-0.35} & -3.70^{+0.62}_{-0.80} & -1.24^{+0.27}_{-0.22} \\
    3.88 & 3.90 & 3.70 & 4.10 & 628 & -7.92^{+0.12}_{-0.10} & -27.26^{+0.14}_{-0.12} & -4.81^{+0.34}_{-0.39} & -2.07^{+0.10}_{-0.09} \\
    4.35 & 4.40 & 4.10 & 4.70 & 442 & -8.32^{+0.29}_{-0.26} & -27.38^{+0.38}_{-0.31} & -4.19^{+0.41}_{-0.47} & -2.20^{+0.16}_{-0.13} \\
    4.92 & 5.10 & 4.70 & 5.50 & 263 & -9.02^{+0.29}_{-0.22} & -27.88^{+0.36}_{-0.27} & -4.51^{+0.66}_{-0.83} & -2.31^{+0.11}_{-0.08} \\
    6.00 & 6.00 & 5.50 & 6.50 & 66 & -10.60^{+0.71}_{-1.06} & -29.12^{+1.04}_{-1.78} & -4.99^{+0.72}_{-1.22} & -2.40^{+0.10}_{-0.08} \\
    \hline
  \end{tabular}
\end{table*}

@@

Figure~\ref{fig:evoln} reveals further potentially systematic errors.
The behaviour of BOSS quasars, shown by open circles in
Figure~\ref{fig:evoln} at redshifts $z=2$--$4$ is striking.  In this
redshift range covered by BOSS the values of the four double power law
parameters deviate from the general trends.  The faint end of the
luminosity function of the BOSS quasars is much shallower and the
break luminosity is fainter by a magnitude compared to the general
trend expected from a smooth evolution.  The bright end of the
luminosity function of quasars in this sample is also much flatter
than that for other samples.  The conspicuousness of the deviation of
the BOSS sample from the general trends makes it unlikely that the
luminosity function evolution indicated by BOSS in the redshift range
$z=2$--$3$ is physical.  Indeed, in this redshift range BOSS quasar
selection is known to be affected by a colour bias
\citep{2011ApJ...728...23W}, which can make estimating completeness
difficult \citep{2006AJ....131.2766R}.

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
    % mosaic.py 
  \end{center}
  \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, the yellow
    curves show the best-fit double power law luminosity function in
    that redshift bin.  Other curves show the three global evolution
    models.  Shaded regions show the one-sigma (68.26\%)
    uncertainties.}
  \label{fig:mosaic_global}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    models.  The symbols show the best-fit parameters with one-sigma
    (68.26\%) uncertainties in redshift bins from
    Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected by
    systematics and removed from the global analysis are shown in
    grey.  In each panel, the solid curves and shaded regions show the
    three best-fit global models with one-sigma uncertainties.
    Model~1 provides a better fit, but requires a rapid change in the
    faint-end slope at $z\sim 3.5$.}
  \label{fig:evoln_global}
\end{figure*}

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
    % rhoqso.py -- draw_withGlobal_multiple()
  \end{center}
  \caption{AGN number density evolution in the global model, when the
    luminosity function is integrated (from top to bottom) down to
    $M_\mathrm{1450}=-18, -21, -24,$ and $-27$.  Filled black circles
    show the estimates from the best-fit double power law luminosity
    functions in various redshift bins, with vertical error bars
    denoting one-sigma (68.26\%) uncertainties.  Open circles show the
    same in redshifts bins affected by systematics.  Curves show the
    estimated density from the global models, with the accompanying
    shaded regions denoting the one-sigma uncertainty. }
  \label{fig:rhoqso}
\end{figure}

@@

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.47\textwidth]{emissivity_18.pdf} & 
      \includegraphics[width=0.47\textwidth]{emissivity_21.pdf} \\
      % gammapi.py -- draw_emissivity()
    \end{tabular}
  \end{center}
  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
    fraction down to a limiting magnitude for a luminosity function
    integration limit of $M_{1450}=-18$ (left panel) and
    $M_{1450}=-21$ (right panel).  Black filled circles with error
    bars in both panels show the emissivity determinations in redshift
    bin deemed to have low systematic errors.  Open circles show
    emissivities for redshift bins that we remove from analysis due to
    high systematic errors.  Solid red curves in both panels show the
    best fit emissivity evolution model, with the shaded area showing
    the one-sigma (68.26\%) uncertainty.  Also shown for comparison in
    both panels are models by \citet[pentagon
      symbol]{2009A&A...507..781S}, \citet[star]{2012ApJ...755..169M},
    \citet[square]{2015AA...578A..83G},
    \citet[triangle]{2018PASJ...70S..34A},
    \citet[circle]{2018AJ....155..131M},
    \citet[diamond]{2018MNRAS.474.2904P}, \citet[open
      rectangle]{2017ApJ...847L..15O}, \citet[dotted green
      curve]{2015ApJ...813L...8M}, \citet[dashed
      brown]{2012ApJ...746..125H}, \citet[dashed
      grey]{2017MNRAS.466.1160M}, \citet[dashed
      blue]{2013A&A...551A..29P}, \citet[solid
      cyan]{2016A&A...587A..41P}, and \citet[solid
      blue]{2017A&A...608A..64C}}.
  \label{fig:e912_2}
\end{figure*}

\subsection{Evolution of the luminosity function}
\label{sec:global}

The smooth evolution of the luminosity function parameters apparant in
Figure~\ref{fig:evoln} suggests that it should be possible to describe
the quasar UV luminosity function evolution out to $z\sim 7$ using
fewer parameters.  Such descriptions have been developed in the
literature for the X-ray \citep[e.g.,][]{2015MNRAS.451.1892A} and
bolometric luminosity functions \citep[e.g.,][]{2007ApJ...654..731H}.
Such ``global'' models of the luminosity function evolution are useful
as they give a continuous description of the luminosity function.
This allows one to reduce the bias introduced by binning the data in
arbitrary redshift bins.  By potentially allowing for extrapolations
beyond the redshift range spanned by the data, such models are
valuable for understanding of the physics behind the luminosity
function.  Ideally, one would want to use physically meaningful
parameters that govern the formation and evolution of the AGN
population.  Unfortunately, such physical parameterisation is yet to
be developed.  We therefore set up an empirical parameterisation to
describe the evolution of the four parameters of the double power law
model in Equation~(\ref{eqn:dpl}) as
\begin{align}
  &\phi_*(z) = f_0(\{c_{0,i}\}, z)\nonumber\\
  &M_*(z) = f_1(\{c_{1,i}\}, z)\nonumber\\
  &\alpha(z) = f_2(\{c_{2,i}\}, z)\nonumber\\
  &\beta(z) = f_3(\{c_{3,i}\}, z),
\label{eqn:global}
\end{align}
where the $c_{j,i}$'s are the new model parameters, and the $f_j$'s
are functions that vary smoothly with redshift $z$.  The joint
posterior probability distribution of these parameters can be now
written as
\begin{equation}
  p(\{c_i\} | \{M_i, z_i\}) \propto p(\{c_i\})p(\{M_i, z_i\} | \{c_i\}),
\end{equation}
where the likelihood 
\begin{equation}
  \mathcal{L}\equiv p(\{M_i, z_i\} | \{c_i\}),
\end{equation}
is now given by $\phi(M,z)$ with suitable normalisation.  Note that
$\phi(M,z)$ is given by Equation~(\ref{eqn:dpl}), but now the four
parameters in that equation are redshift-dependent, so that
\begin{multline}
  \phi(M,z) = \phi_*(z) \left[10^{0.4(\alpha(z)+1)(M-M_*(z))}\right. \\ \left.+ 10^{0.4(\beta(z)+1)(M-M_*(z))}\right]^{-1}.
\end{multline}
The negative logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ is
a straightforward generalisation of Equation~(\ref{eqn:S}), given by
\begin{multline}
  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
  \label{eqn:S2}
\end{multline}
where now $N$ is the total number of quasars included in the analysis,
and the integrals in the second term on the right-hand side are over
the complete surveyed range of luminosity and redshift, instead of
redshift and luminosity bins.  We consider models in which the
evolution of the four double power law parameters is modelled
independently as in Equations~(\ref{eqn:global}), an approach
sometimes termed as ``flexible double power law''
\citep{2015MNRAS.451.1892A}.  We present three such models in this
paper.  These are shown in Figure~\ref{fig:evoln_global}.  The three
models differ in the way they describe the evolution of the faint-end
slope $\beta$ and in the selection of the AGN data.  The models are
defined as follows.
